A Kochen-Specker system has at least 22 vectors

### 2014-12-11 paper/main.tex
Add comp7 & fix some text
Signed-off-by: Bas Westerbaan <bas@westerbaan.name>

\begin{proposition}\label{prop:ks-enoughtriangles}
    In a minimal Kochen-Specker graph,
        every node is part of a triangle.
\end{proposition}
\begin{proof}
    Given any graph~$G$ together with a vertex~$v$ of~$G$
        such that~$v$ is not part of a triangle.
    Let~$G'$ denote~$G$ without~$v$.
    Suppose~$G'$ is~$010$-colorable.
    Then so is~$G$, as we may extend the coloring of~$G'$
        to~$G$ by coloring~$v$ with~$0$.
    Contraposing: if~$G$ is not~$010$-colorable,
        then~$G'$ is not~$010$-colorable.
    Clearly, if~$G$ is embeddable, then so is~$G'$.
    Thus if~$G$ is Kochen-Specker, then so is~$G'$.
\end{proof}
There are only TODO squarefree non-isomorphic 
graphs on 17 vertices with minimal vertex degree 3
where every node is part of a triangle.
Unfortunately,
we could not find an efficient algorithm
to restrict the enumeration of graphs
to those where every node is part of a triangle.

>>>>

\begin{proposition}\label{prop:ks-enoughtriangles}
    In a minimal Kochen-Specker graph,
        every vertex is part of a triangle.
\end{proposition}
\begin{proof}
    Given any graph~$G$ together with a vertex~$v$ of~$G$
        such that~$v$ is not part of a triangle.
    Let~$G'$ denote~$G$ without~$v$.
    Suppose~$G'$ is~$010$-colorable.
    Then so is~$G$, as we may extend the coloring of~$G'$
        to~$G$ by coloring~$v$ with~$0$.
    Contraposing: if~$G$ is not~$010$-colorable,
        then~$G'$ is not~$010$-colorable.
    Clearly, if~$G$ is embeddable, then so is~$G'$.
    Thus if~$G$ is Kochen-Specker, then so is~$G'$.
\end{proof}
There are only~${\sim}10^5$ squarefree non-isomorphic 
graphs on 17 vertices with minimal vertex degree 3
where every vertex is part of a triangle.
Unfortunately,
we could not find an efficient algorithm
to restrict the enumeration of graphs
to those where every vertex is part of a triangle.
